### 2023-11-07 main.tex
check

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\bm{\xi}=\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
 namely the joint probability of having, for all $k=1,\ldots,m$, $t_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-t_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})\dt

@@

	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}\dt

@@

The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 
		\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})\dt

@@

		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\dt

@@

		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)\dt

@@

The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})\dt

@@

	\langle n_{a_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}

@@

	\frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}

@@

	\frac{(L-y_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}

@@

	\frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}

@@

	\frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}

@@

	\frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt

@@

	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\nonumber\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]\nonumber
	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\dt

@@

This formula will be useful in the following. 

>>>>

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\bm{\xi}=\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
 namely the joint probability of having, for all $k=1,\ldots,m$, $t_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-t_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$ reads
\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,x_{1},c_{1})\dt

@@

	\langle \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt

@@

The two-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 
		 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},c_{2})\dt

@@

	 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt

@@

		 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{2}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt

@@

The three-point correlations with respect to the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$
 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{3}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{3})\dt

@@

 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}

@@

	\frac{(L+1-x_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-x_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}

@@

	\frac{(L-x_{2})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}

@@

	\frac{(L-x_{1})(L-x_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}

@@

	\frac{(L-x_{1})(L-x_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}

@@

	\frac{(L-x_{1}-1)(L-x_{2})(L-x_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt

@@

	&\mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]-\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber
	=&-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt

@@

Equation \eqref{ABS_1} will be useful in the following. 
